Figures

### 2019-08-05 figures/07_model-selection.Rmd
towards viz of global re

>>>>

```{r re-comparison}

# tp, tn
# ag, row_crop, pasture, corn, soybeans
re_global <- dplyr::rbind_all(lapply(re_brms, function(x) x$re_global))
re_global$term <- unlist(lapply(re_brms, 
                                function(x) get_re_text(as.character(x$formula)[1])))
re_global$response <- c(rep("tp", 5), rep("tn", 5))
re_global <- dplyr::filter(re_global, term != "rowvcropvpct")

loo_compare(
  loo(re_brms[[1]]), 
  loo(re_brms[[2]]), 
  loo(re_brms[[3]]), 
  loo(re_brms[[4]]), 
  loo(re_brms[[5]]) 
)

loo_compare(
  loo(re_brms[[6]]), 
  loo(re_brms[[7]]), 
  loo(re_brms[[8]]), 
  loo(re_brms[[9]]), 
  loo(re_brms[[10]]) 
)

group_by(re_global, response) %>%
  arrange(desc(`50%`))

ggplot(data = re_global) +
  geom_pointrange()
